Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-03-11 ms.tex
fixed discussion of scatter in lx

Perhaps a more readily addressable test is whether a steady-state accretion
picture can account for the the large scatter, typically of $2-3$ orders of magnitude, in $L_{X}/L_{\rm
  edd}$ at fixed $M_{\bullet}$.  Scatter could result from at 
least three effects: (1) instric scatter in the scaling relationships ($\Mbh-\sigma$ and $\Mbh-L_{\rm
  bulge}$) used to measure $\Mbh$; (2) the strong sensitivity of the accretion rate to
the stellar wind velocity, $\dot{M}/\dot{M}_{\rm edd} \propto
v_{w}^{-3.8(-2.4)}$ for core(cusp) galaxies, respectively
(Fig.~\ref{fig:mdot_mass}; eq.~[\ref{eq:eddr_analytic}]).  When 
combined with the significant dependence of $v_w$ on stochastic
intermittency in the star formation history (Appendix \ref{fig:NickPlot2}), this can lead to order of magnitude differences in $\dot{M}$; (3) possible differences angular momentum of the infalling gas and consequentiallly the
efficacy of disk outflows may vary from galaxy to galaxy at fixed
$\Mbh$.  Also potentially contributing is the order of magnitude difference, at fixed $v_w$ and $M_{\bullet}$, between $\dot{M}$ for core and cusp galaxies at fixed $v_w$ (Fig.~\ref{fig:bh_growth}) which could also lead to
scatter of $\dot{M}$ due to the variation in the Nuker stellar density
profile $\Gamma$ at fixed $M_{\bullet}$.  Any such differences in $\dot{M}$ are exacerbated by the expectation
that $L_{\rm X} \propto \dot{M}^{2} $ for radiatively inefficient
flows.

>>>>

Perhaps a more readily addressable test is whether a steady-state accretion
picture can account for the the large scatter, typically of $2-3$ orders of magnitude, in $L_{X}/L_{\rm
  edd}$ at fixed $M_{\bullet}$.  Scatter could result from at 
least three effects: (1) instric scatter in the scaling relationships ($\Mbh-\sigma$ and $\Mbh-L_{\rm
  bulge}$) used to measure $\Mbh$; (2) the strong sensitivity of the accretion rate to
the stellar wind velocity, $\dot{M}/\dot{M}_{\rm edd} \propto
v_{w}^{-3.8(-2.4)}$ for core(cusp) galaxies, respectively
(Fig.~\ref{fig:mdot_mass}; eq.~[\ref{eq:eddr_analytic}]).  When 
combined with the significant dependence of $v_w$ on stochastic
intermittency in the star formation history (Appendix \ref{fig:NickPlot2}), this can lead to order of magnitude differences in $\dot{M}$; (3) differences angular momentum of the infalling gas from galaxy to galaxy, resulting in differences in the fraction of the gas lost to outflows, $\Mbh$.  Also potentially contributing is the order of magnitude difference, at fixed $v_w$ and $M_{\bullet}$, between $\dot{M}$ for core and cusp galaxies (Fig.~\ref{fig:bh_growth}).  Differences in $\dot{M}$ are augmented by the expectation that $L_{\rm X} \propto \dot{M}^{2} $ for radiatively inefficient flows.
